\section{Background}
\suppressfloats[t]

\subsection{ZNS Placement and Write Amplification}

\zns SSDs expose a storage interface in which each zone is written sequentially and later reset as a unit~\cite{zns}.  This interface removes part of the hidden device FTL policy and gives the host more control over placement.  The benefit depends on grouping objects with compatible lifetimes.  When a zone contains only expired objects, reset is cheap.  When a zone also contains live objects, the host must copy those valid blocks elsewhere before reset, increasing write amplification factor (WAF).

Prior placement systems therefore focus on predicting block invalidation time.  \sepbit separates data using historical invalidation behavior.  \midas adapts group configuration to workload patterns.  \dogi combines hot filtering, learned invalidation-time prediction, GC relocation policy, and dynamic group organization.  The DOGI paper evaluates both static-skew workloads such as FIO Zipf and YCSB-A/F and dynamic workloads such as Varmail, Alibaba, and Exchange~\cite{dogi}.  This is the right baseline family for \system because these systems represent the strongest storage-history approach.

\subsection{Host-Guided Placement Interfaces}

\system is a lifecycle-placement policy, not a claim that native \zns is the only possible interface.  Native \zns is the right first substrate because the host directly controls zone append, zone close, valid-block migration, and reset timing.  That makes WAF, reset eligibility, zone fill, and stale-secret exposure auditable in the evaluation.  Flexible Data Placement (FDP) exposes a different host-guided interface: the host supplies placement handles while the device keeps a conventional block interface and performs internal grouping~\cite{fdp}.

\begin{table}[!b]
\centering
\caption{QUASAR can target both native \zns and FDP-like host-guided placement.  The paper evaluates \zns first because it exposes reset and migration accounting directly.}
\label{tab:interfaces}
\footnotesize
\begin{tabularx}{\columnwidth}{lYY}
\toprule
\textbf{Interface} & \textbf{QUASAR mapping} & \textbf{Boundary} \\
\midrule
Native \zns & Zone family from \texttt{intent}, \texttt{epoch\_id}, and security class. & Host-visible append/reset accounting. \\
FDP & Placement handle from hashed intent, epoch/cohort, security, and tenant. & Device-internal reclaim is less observable. \\
Fallback block path & Payload or low-confidence writes use history placement. & No strong reset eligibility claim. \\
\bottomrule
\end{tabularx}
\end{table}

Table~\ref{tab:interfaces} gives the deployment boundary.  FDP can carry the same semantic grouping signal, but limited placement handles require hashing, binning, or admission control, and device-internal reclaim makes stale-exposure accounting less direct.  We therefore use \zns for the main experiments and treat FDP as the natural deployment extension.

\subsection{Post-Quantum Object Lifetimes}

Post-quantum workloads introduce a different kind of lifetime signal.  A KEM artifact or secret-bearing recovery record is not short-lived because it has a particular LBA pattern; it is short-lived because the cryptographic protocol invalidates it.  A signature log may be append-only and long-lived, while a KMS envelope may die when an epoch closes.  A certificate metadata object may follow a rotation period rather than a session boundary.  These differences exist within the same service and often within the same burst of I/O.

\begin{table}[!b]
\centering
\caption{Post-quantum objects have different lifetime and security behavior even when they are generated by the same service.}
\label{tab:pqc-objects}
\footnotesize
\begin{tabularx}{\columnwidth}{lYY}
\toprule
\textbf{Object} & \textbf{Lifetime driver} & \textbf{Placement implication} \\
\midrule
KEM artifact & Session or epoch close & Group by epoch; reset quickly. \\
Secret-bearing record & Session close & Isolate from payload and logs. \\
KMS envelope & Key epoch & Pack with same epoch family. \\
Certificate metadata & Rotation policy & Use rotation-zone family. \\
Signature log & Retention policy & Append-only placement. \\
Payload & Application update pattern & Use history-based fallback. \\
\bottomrule
\end{tabularx}
\end{table}

Table~\ref{tab:pqc-objects} gives the placement consequence.  A single hotness label cannot safely place these objects because two objects with similar write frequency may have opposite reclaim requirements.  Conversely, two objects with different LBAs and different sizes may be ideal zone neighbors if they die at the same epoch boundary.

\noindent\textbf{Threat model for stored PQC state.}
\system does not require every TLS session key to be synchronously persisted.  Many deployments correctly keep raw session secrets only in RAM or in an HSM.  The target is narrower: services that already persist bounded PQC lifecycle state, such as KMS envelopes and key-wrap records, crash-recovery or session-ticket state, compliance/audit records, certificate and signature metadata, or constrained edge spill paths.  If a deployment emits no secret-bearing or lifecycle-bound PQC writes, \system falls back to payload placement and makes no security improvement claim.

\subsection{Claim Boundary}

\system is not an oracle.  It does not receive a future deletion timestamp for every object, and it does not assume that every hint is perfect.  The hint expresses lifecycle class and epoch membership, not secret key material.  Correctness is protected by a conservative epoch manager: a zone family is reset only after the manager confirms that all objects in that family have expired or have been safely migrated.

The security claim is also scoped.  Zone reset makes a zone reusable and can reduce exposure, but it is not by itself NIST-style media sanitization.  NIST SP 800-88 Rev. 2 defines sanitization around making target data access infeasible for the relevant effort level~\cite{nist-sp80088r2}; a \zns reset only changes host-visible zone state unless the device also provides stronger erase semantics.  Our physical device advertises crypto-erase and block-erase sanitize support, and the crypto-erase sanitize command path has been executed successfully.  This validates that the destructive command path exists on the device; it does not make sanitize a safe per-zone operation for a shared namespace.  The default claim is therefore reset eligibility, logical isolation, and exposure-window reduction.  A physical erase claim requires an erase scope that matches the target cohort, such as a dedicated namespace or media pool, per-cohort encryption-key isolation, or future per-zone erase semantics~\cite{nvme-sanitize}.
