\section{Implementation}

\subsection{Trace and Replay Infrastructure}

We implemented \system as a trace-driven allocator and actual-\zns replay framework.  The trace format records writes, expirations, object identifiers, sizes, LBA-like payload location, intent, epoch, security class, tenant, and confidence.  The same trace is replayed through FIFO, \sepbit-style, \midas-style, \dogi-style, \system, and \system-\dogi hybrid policies.  This keeps timing and object lifetimes identical across policies.

The implemented deployment hook is intentionally small: a TLS terminator, KMS, logging component, or privileged policy layer emits the 32-byte \texttt{quasar\_hint} when it writes a KEM artifact, secret-bearing recovery record, certificate record, key-wrap record, or signature log.  In the prototype, this hint is carried in the JSONL trace and in the user-space request context that drives the physical replay.  This is equivalent to a kernel-bypass SPDK/xNVMe request-context design in terms of allocator input, but it is not a full SPDK poll-mode implementation.  Kernel integration would use one of the attachment points in Table~\ref{tab:hint-delivery}; untrusted writers cannot directly allocate exact secret families because the policy layer validates provenance and quota before the allocator sees the hint.

The workload generators produce three classes of traces.  First, DOGI-paper-shaped traces mirror the workload axes described by DOGI: FIO Zipf, YCSB-A, YCSB-F, Varmail, Alibaba, and Exchange.  Second, pressure traces increase PQC density and reduce free-zone slack to force GC.  Third, hostile traces introduce missing hints, wrong epochs, tenant pressure, and stragglers.  The implementation also includes a real FIO iolog converter that maps benchmark-issued FIO writes into the same QUASAR JSONL schema before adding PQC lifecycle side writes.  To close the application-trace realism gap, we additionally captured a real sysbench fileio block trace with \texttt{blktrace} while a liboqs KMS/audit side writer persisted PQC lifecycle records.  That artifact proves the trace-collection path for real application I/O plus PQC side writes; it is not presented as a full SPDK/ZenFS end-to-end latency result.

\subsection{Baseline Implementations}

The same-path comparison implements FIFO, \sepbit-style, \midas-style, and \dogi-style policies in the replay framework.  These implementations are intentionally described as style-compatible baselines because they share the same physical packed-\zns path as \system.  The artifact set also contains exact public DOGI/MiDAS/SepBIT runs in their native environments.  We keep these exact runs separate from the same-path results because their units and internal segment models are not identical to the packed replay path.

\subsection{Physical ZNS Path}

The actual-\zns experiments use a Western Digital ZN540-class \zns NVMe SSD mounted with \texttt{zonefs}.  The replay writes zone files sequentially and issues reset-like truncation or helper operations according to the policy plan.  This path measures full-suite append/reset accounting, but it includes zonefs helper overhead.  We therefore report it as actual-\zns replay overhead, not as final production p99 latency.

To check the lower-overhead command path, we also implemented an xNVMe raw \zns latency probe.  The local xNVMe backend uses Linux NVMe ioctl synchronous commands.  It bypasses the zonefs helper path and completes 4,096 4KiB appends with p99 append latency of 26,064 ns.  This is not an SPDK poll-mode result, but it bounds the helper-path caveat.

\subsection{Security Capability Check}

The physical device reports sanitize capability with crypto-erase and block-erase support.  We executed an NVMe crypto-erase sanitize command on the device and observed successful completion in the sanitize log.  This validates the destructive command path, but it is not a per-zone or per-epoch erase primitive for a shared namespace.  The evaluation keeps this separate from zone reset: \system makes secret-bearing zones eligible for host-visible reset, and the per-cohort key-isolation artifact validates a cohort-scoped crypto-erase path by destroying one epoch key while preserving unrelated cohorts.  Hardware physical erasure would still require an isolated namespace/media pool or hardware erase semantics with cohort-sized scope.
