\section{Discussion and Limitations}

\noindent\textbf{QUASAR is not a universal WAF optimizer.}
Easy rows deliberately show \dogi-style WAF near 1.0; there, \system's benefit is exposure reduction.  The scoped claim is that PQC death cohorts are invisible to history-based placement and become costly under pressure, not that \system wins every trace.

\noindent\textbf{Correctness, trust, and tenancy.}
Wrong or missing hints must not cause data loss: \system resets only after epoch-close confirmation; otherwise it migrates residuals, downgrades to normal GC, or sends low-confidence writes to overflow.  High-priority secret placement is emitted by trusted TLS/KMS/logging or policy components, with opaque cohort IDs, tenant-local namespaces, quotas, and admission limits to prevent priority inflation.

\noindent\textbf{Resource tradeoffs are explicit.}
Dedicated epoch zones can waste space, and strict zero-wait residual handling can be expensive on hostile rows such as YCSB-F p8000.  The default hybrid reserves exact placement for high-security cohorts, bins sparse cohorts, sends uncertain writes to overflow, and makes strict tenant/residual modes opt-in.

\noindent\textbf{ZNS and FDP deployment.}
\system should be read as a protocol-lifetime placement policy, not as a claim that every deployment must expose native \zns.  Native \zns gives the paper direct host-visible append, reset, fill, and migration accounting.  FDP can carry the same grouping signal through placement handles, but handle scarcity, hashing collisions, and device-internal reclaim reduce observability.  A production deployment can therefore choose native \zns for host-managed reset or FDP for lower integration friction, while keeping the same admission and overflow rules.

\noindent\textbf{Device and deployment boundaries.}
Zone reset alone is not physical NAND erasure.  Strong erasure requires semantics whose blast radius matches the cohort being destroyed.  A shared-namespace NVMe sanitize/crypto-erase command can be too broad: it may invalidate unrelated payload or tenant data and therefore cannot be treated as a per-zone epoch cleanup operation.  Our per-cohort DEK artifact demonstrates one deployable crypto-erase scope: destroying one cohort key makes only that cohort cryptographically inaccessible while other cohorts remain decryptable.  The physical evidence uses one WD ZN540-class device, zonefs replay, liboqs/OpenSSL traces, a TLS socket trace, a Sysbench/MySQL execution gate, per-cohort key-isolated crypto erase, and an xNVMe probe.  Exact DOGI/MiDAS/SepBIT runs stay separate because their units differ from packed actual-\zns replay.  We report host-visible resets/utilization and cohort-scoped crypto-erase feasibility, but not chip-off erasure, internal wear telemetry, full application p99 latency, real DB block traces, FDP hardware behavior, hardware per-zone erase, or full SPDK poll-mode replay.
